Marginalization of photometric redshift uncertainties

### 2020-05-15 Paper/paper.tex

\subsubsection{Cosmic Variance in calibrator sample}

@@

\section{Appplication to HSC clustering data}
\label{sec:hsc}

>>>>

\subsubsection{Cosmic Variance in calibrator sample}
The covariance matrix between two tomographic bins is given by:
\begin{equation}
Cov_{ij}=\frac{N_i N_j}{2\pi^2} \int_0^\infty dk_\parallel \cos(k_\parallel(\chi_i-\chi_j))\int_0^\infty dk_\perp k_\perp W_i(k_\parallel,k_\perp)W_j(k_\parallel,k_\perp)P_{\bf gg}({\bf k}),
\end{equation}
where we can model the power spectra at each bin centre and for all
transverse and parallel modes using the Kaiser formula (CITE), which corrects for redshift space distortions through
the expression:
\begin{equation}
P_{gg}({\bf k},z)=\left(b_g(z)+f(z)\frac{k_\parallel^2}{k^2}\right)^2\,P_{mm}(k,z),
\end{equation}
where $f(z)$ is
the logarithmic growth
rate
and the
evolution of the linear galaxy bias is given by $b_g(z) = 0.95/D(z)$
with $D(z)$ the growth factor.

In this work, we use the galaxy sample in the COSMOS survey as calibrator, which
covers a total area of
$A_{\rm sky} = 1.7 \ {\rm deg}^2$ for galaxies with redshifts $z < 2$.
We model the window function for each bin of the dataset through:
\begin{equation}
W(k_\parallel,k_\perp)=j_0(k_\parallel\Delta\chi/2)\,\frac{2 J_1(k_\perp R_{\rm mean})}{k_\perp R_{\rm mean}},
\end{equation}
where $R_{mean}$ is the
physical size of the survey measured at the mean
distance to the
tomographic bin, 
$R_{\rm mean} = 
\sqrt{\frac{A_{\rm sky}}{\pi}} \chi_{\rm mean}$.
We assume that the
cosmic covariance
between the tomographic bins is negligible, so we estimate the cosmic variance covariance matrix by
treating each bin independently. We show the resulting correlation matrix of the COSMOS cosmic variance in Fig. \ref{fig:CV}.

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{Paper/corr_CV_0.png}
\caption{Cosmic variance (CV) correlation matrix with subtracted diagonal for the first tomographic bin of the HSC data.} 
\label{fig:CV}
\end{figure}

@@

\section{Appplication to HSC clustering data}
\label{sec:hsc}
\an{Some citations are currently missing but I will put them in later.}
We apply the method outlined above to the data obtained in Ref.~\cite{1912.08209}. This work measured the angular galaxy clustering power spectrum from HSC DR1 data. In the following, we give a very brief summary of the methodology employed in this work and refer the reader to Ref.~\cite{1912.08209} for more details.
\subsection{Background theory}
The angular clustering signal for galaxies in redshift bins $i, j$ with photo-$z$ distributions $p^i(z), p^j(z)$ can be modeled using the Limber approximation as \cite{1953ApJ...117..134L, 1992ApJ...388..272K, Kaiser:1998}
    \begin{equation}\label{eq:cell_gg_limber}
      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)} p^i(z)p^j(z)\,P_{gg}\left(z,k=\frac{\ell+1/2}{\chi(z)}\right),
    \end{equation}
where $P_{gg}(z,k)$ denotes the underlying 3D galaxy power spectrum, $\chi(z)$ is the comoving distance and $H(z)$ denotes the Hubble parameter at redshift $z$. As can be seen from Eq.~\ref{eq:cell_gg_limber}, the spherical harmonic power spectrum $C_{\ell}$ depends linearly on the photometric redshift distributions $p^i(z)$, which facilitates the computation of the $T$ matrix defined above.

We follow Ref.~\cite{1912.08209} and compute theoretical predictions for the galaxy power spectrum $P_{gg}(z,k)$ within the halo model combined with halo occupation distribution modeling \cite{2000MNRAS.318.1144P,2002PhR...372....1C,2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}. 
\subsection{The HSC dataset}
The Hyper-Suprime Cam survey is an on-going photometric galaxy survey survey focused mainly on weak gravitational lensing. The analysis in Ref.~\cite{1912.08209} is based on the publicly-available HSC DR1 data, whose so-called wide fields cover approximately 108 square degrees on the sky, subdivided into seven distinct patches. Ref.~\cite{1912.08209} used these data to compute spherical harmonic galaxy clustering power spectra for four tomographic redshift bins between $z=0.15$ and $z=1.5$, taking both auto- and cross-correlations into account. These power spectra have been corrected for observational and extragalactic systematics by deprojection at the map-level \cite{2019MNRAS.484.4127A}. Finally, following Ref.~\cite{2019PASJ...71...43H}, photometric redshift distributions have been estimated by cross-matching HSC galaxies to galaxies in the COSMOS 30-band photometric catalog presented in Ref.~\cite{2016ApJS..224...24L}.
\subsection{Validating the linear expansion}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.2\textwidth]{Paper/Tmat.png}
\caption{Visualization of the derivative matrix $T_{mn} = {\partial t_m}/{\partial N_n}$. \todo{Make look nicer: split into tomo bins}} 
\label{fig:Tmat}
\end{figure}

\begin{itemize}
  \item Plot showing $T$
  \item Plot showing exact $C_\ell$ vs linear prediction. \todo{Make your plots into subplots; verify the Tmatrix}
\end{itemize}{}
\subsection{Impact of N(z) uncertainties on final parameters}

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{Paper/corr_data.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.\linewidth]{Paper/corr_diff.png}
  \label{fig:sub2}
\end{subfigure}
\caption{Correlation matrix for the fiducial HSC dataset (\textit{left}) and difference with its marginalized version (\textit{right}).}
\label{fig:fid_marg_cov}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{Paper/triangle_fid_marg.png}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using the covariance matrix from the full HSC dataset (\textit{red}) and from its marginalized version (\textit{blue}).}
\label{fig:triangle_fid_marg}
\end{figure}

\begin{figure}[ht]
\centering  
\includegraphics[width=1.\textwidth]{Paper/triangle_marg_tests.png}
\caption{Triangle plot with constraints of the 6 HOD parameters obtained using different choices for the marginalized covariance matrix: in \textit{green} is shown the result where the diagonal noise is set to a very large value ($A_{\rm noise} = 42$); in \textit{gray} is shown the case where the marginalization is performed assuming fiducial HOD-model values which are $1\sigma$ away from their posterior mean values taken from \todo{CITE Andrina's paper}; in \textit{red} is shown the case where the smoothing has been removed ($A_{\rm smooth} = 0$); and finally in \textit{blue} is shown the fiducial case with $A_{\rm noise} = 4$ and $A_{\rm smooth} = 0.25$.}
\label{fig:triangle_marg_tests}
\end{figure}

Plots showing the effects of different things:
\begin{itemize}
\item Compare different choices of prior (smoothness, no smoothing, different degrees of noise etc.)
\item Triangle plot with T matrix computed from a different fiducial.
\item Compare CV-only covariance vs. no covariance.
\item Compare old marginalization vs. new one (maybe same plot).
\item Compare old marginalization with CV priors (importance sample).
\end{itemize}

Other results:
\begin{itemize}
  \item smoothness does nothing
  \item quote $\chi^2$ values \todo{Make a table}
\end{itemize}

\begin{center}
 \begin{tabular}{c | c c c} 
 \hline\hline
 Parameter & HSC covariance, full & HSC covariance, HOD & Marginalized covariance, HOD \\ [0.5ex] 
 \hline
 $\chi^2/\nu$ & 87.49/80 & 94.97/88 & 91.06/88 \\

 $\mu_{{\rm min},p}$ & -0.52 & -1.47 & -1.42 \\

 $\mu_{\rm min}$ & 11.88 & 11.73 & 11.73 \\

 $\mu_{0,p}$ & 1.68 & 4.86 & 5.03 \\

 $\mu_{0}$ & 0.02 & 11.53 & 11.41 \\

 $\mu_{1,p}$ & 0.87 & -0.58 & -0.51 \\

 $\mu_{1}$ & 13.073 & 12.866 & 12.873 \\ [1ex] 
 \hline
 \hline
\end{tabular}
\end{center}
%[-1.42408101 11.73454764  5.0302023  11.41301207 -0.50980494 12.87323354]
%[-1.47048791 11.73097558  4.85774675 11.52813388 -0.58053445 12.86613972]
%[ 2.18173486e-02 -1.39414027e-02 -4.61928378e-03  1.27879857e-02
% -5.18739083e-01  1.18844059e+01  1.67767553e+00  2.01822301e-02
%  8.65219859e-01  1.30726966e+01 -1.64307267e-01 -3.19342441e-02
%  3.97310971e-02  3.88321407e-02]
